---
title: "p8105_hw1_yw3608"
author: "Yuxuan Wang"  
date: "9/29/2021"
output:
  github_document
---
I'm yw3608's homework1! 

# Problem 1
**First, load the tidyverse library.**
```{r,results= 'hide',message=FALSE}
library(tidyverse)
```

**Next, create a dataframe which satisfy the required question**

```{r}

df = 
  tibble(
    score=rnorm(10,mean=0,sd=1),
gr_than_zero =score > 0,
vec_char =c("Lily","Cody","Tommy","Sally","Jack","Anna","Lucy","Coco","Jerry","Stella"),
vec_factor =factor(c("high school diploma","college diploma","college diploma","college diploma","college diploma","college diploma","high school diploma","postgraduate diploma","postgraduate diploma","high school diploma"))
)
df
```


**Next, try to take the mean of each variable in my dataframe**

```{r,collapse=TRUE,message=FALSE ,warning =FALSE}
mean(pull(df,score))
mean(pull(df,gr_than_zero))
mean(pull(df,vec_char))
mean(pull(df,vec_factor))

```


```{r}
#Here, we can take the mean of a random sample of size 10 from a standard Normal distribution
#We can also take the mean of logical vector indicating whether elements of the sample are greater than 0
#We cannot take the mean of  character vector of length 10
#We can not take the mean of a factor vector of length 10, with 3 different factor “levels”**

```


**Next, convert variables from logical vector, character and factor  to numeric by using the as.numeric function. Outputs are hide as instructed.**

```{r,warning = FALSE ,results='hide' } 
as.numeric(df$gr_than_zero)
as.numeric(df$vec_char)
as.numeric(df$vec_factor)

```

```{r}
#By using as.numeric function, the logical vector changed to either 0 or 1, which means that TRUE OR FALSE. 
#The character vector still shows the warning message which can explain the warning message as 
#I tried to take the mean of it.Argument is not numeric or logical will return NA.
#The factor vector returns to 1,2 or 3, which is the 3 diffenent levels.
```

# Problem 2
**First, install the palmerpenguins packages,and write a short description of the penguins dataset.**
```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
```

```{r}
#The data in this dataset, including names / values of important variables
#There are in total 8 varialbels.They are species, island,bill_length_mm,bill_depth_mm,flipper_length_mm
#body_mass_g, sex and year.

```

**Secondly, get the size of the dataset by using nrow and ncol.**
```{r,collapse=TRUE}
nrow(penguins)
ncol(penguins)
##There are 344 rows and 8 colums.
```

**Next,get the mean of flipper length.**
```{r,collapse=TRUE}
##Here,I use the na.omit function to omit NA and named the NA-free dataset as penguins_new. 
penguins_new = na.omit(penguins)
mean(pull(penguins_new,flipper_length_mm))
```


